MSDS6371Project

### 2020-11-25 MSDS6371Project.Rmd
update MSDS report

#### Analysis 1:
```{r}
#extract variables we're interested for Analysis 1
data1 = amesHouse %>% dplyr::select(SalePrice,GrLivArea,Neighborhood)%>%
  filter(Neighborhood=="NAmes"|Neighborhood=="Edwards"|Neighborhood=="BrkSide")
str(data1)
#383 observations selected after filtering neighborhood of "NAmes", "Edwards" and "BrkSide"
#Convert Neighborhood to factors
data1$Neighborhood = as.factor(data1$Neighborhood)
#Plot and observe the relationship between SalePrice and GrLivArea
data1 %>% ggplot(aes(x=GrLivArea,y=SalePrice))+
  geom_point()+ggtitle("Sale Price vs. Square Foot of Living area")+
  xlab("Square Foot of Living Area")+
  ylab("Sale Price")
#there are some outliers that may not have come from the same population of interest
#build model to identify the outliers
model1 = lm(SalePrice~GrLivArea,data=data1)
summary(model1)
#Look at residual plots and cook's distance
plot(model1)
cooksDistance = data.frame(distance = cooks.distance(model1))
cooksDistance%>%filter(distance>=1)
ols_plot_cooksd_bar(model1)
ols_plot_resid_stand(model1)
#ols_plot_resid_lev(model1)
# Observation 339 has cook's distance larger than 5.6, Observation 131's cook's D is larger than 1 so it may due to the face it is a unique case.
# Observation 169 and 190 has standarlized residual greater than 4, these two observations can also potentially not coming from the same population of interest
# Since our sample is sufficiently large, deleting these four outliers won't make a huge difference.
# Call these new dataset without outliers data2
data2 = data1[-c(131,169,190,339),]
str(data2)
#build new model to double check
model2 = lm(SalePrice~GrLivArea,data=data2)
summary(model2)
plot(model2)
ols_plot_cooksd_bar(model2)
ols_plot_resid_stand(model2)
#Cook's Distance within roughly 0.1, residual within 3, decent amount of observations beyond 2 (within 5%)
#Assumptions met, move on to include categorical variables
model3 = lm(SalePrice~GrLivArea+Neighborhood+GrLivArea*Neighborhood,data=data2)
summary(model3)
plot(model3)
ols_plot_cooksd_bar(model3)
ols_plot_resid_stand(model3)
#Assumptions are met, model 3 has higher Adjusted R-squared compared to model2

>>>>

#### Analysis 1:
```{r}
#extract variables we're interested for Analysis 1
data1 = amesHouse %>% dplyr::select(SalePrice,GrLivArea,Neighborhood)%>%
  filter(Neighborhood=="NAmes"|Neighborhood=="Edwards"|Neighborhood=="BrkSide")
str(data1)
#383 observations selected after filtering neighborhood of "NAmes", "Edwards" and "BrkSide"
#Convert Neighborhood to factors
data1$Neighborhood = as.factor(data1$Neighborhood)
#Plot and observe the relationship between SalePrice and GrLivArea
data1 %>% ggplot(aes(x=GrLivArea,y=SalePrice))+
  geom_point()+ggtitle("Sale Price vs. Square Foot of Living area")+
  xlab("Square Foot of Living Area")+
  ylab("Sale Price")
#there are some outliers that may not have come from the same population of interest
#build model to identify the outliers
model1 = lm(SalePrice~GrLivArea,data=data1)
summary(model1)
#Look at residual plots and cook's distance
plot(model1)
cooksDistance = data.frame(distance = cooks.distance(model1))
cooksDistance%>%filter(distance>=1)
ols_plot_cooksd_bar(model1)
ols_plot_resid_stand(model1)
#ols_plot_resid_lev(model1)
# Observation 339 has cook's distance larger than 5.6, Observation 131's cook's D is larger than 1 so it may due to the face it is a unique case.
# Observation 169 and 190 has standarlized residual greater than 4, these two observations can also potentially not coming from the same population of interest
# Since our sample is sufficiently large, deleting these four outliers won't make a huge difference.
# Call these new dataset without outliers data2
data2 = data1[-c(131,169,190,339),]
str(data2)
data2 %>% ggplot(aes(x=GrLivArea,y=SalePrice))+
  geom_point()+ggtitle("Sale Price vs. Square Foot of Living area")+
  xlab("Square Foot of Living Area")+
  ylab("Sale Price")
#build new model to double check
model2 = lm(SalePrice~GrLivArea,data=data2)
summary(model2)
plot(model2)
ols_plot_cooksd_bar(model2)
ols_plot_resid_stand(model2)
#Cook's Distance within roughly 0.1, residual within 3, decent amount of observations beyond 2 (within 5%)
#Assumptions met, move on to include categorical variables
model3 = lm(SalePrice~GrLivArea+Neighborhood+GrLivArea*Neighborhood,data=data2)
data2 %>% ggplot(aes(x=GrLivArea,y=SalePrice,color=Neighborhood))+
  geom_point()+ggtitle("Sale Price vs. Square Foot of Living area")+
  xlab("Square Foot of Living Area")+
  ylab("Sale Price")
summary(model3)
plot(model3)
ols_plot_cooksd_bar(model3)
ols_plot_resid_stand(model3)
anova(model3)
confint(model3)
#Assumptions are met, model 3 has higher Adjusted R-squared compared to model2
# Change reference to Edwards to get CI for slope
data2$Neighborhood = relevel(data2$Neighborhood,ref="Edwards")
model3 = lm(SalePrice~GrLivArea+Neighborhood+GrLivArea*Neighborhood,data=data2)
summary(model3)
confint(model3)

# Change reference to NAmes to get CI for slope
data2$Neighborhood = relevel(data2$Neighborhood,ref="NAmes")
model3 = lm(SalePrice~GrLivArea+Neighborhood+GrLivArea*Neighborhood,data=data2)
summary(model3)
confint(model3)
